---
title: "MCMS package introduction"
author: "Xavier Robin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

```{r eval = FALSE}
library(devtools)
devtools::install_github("xrobin/MCMS")
```

The package can later be loaded with 
```{r}
library(MCMS)
```

## Overview

The MCMS workflow has the following steps:

### Read the data

The Label-free data is read from the MaxQuant 1.5 output. Use the `read.labelfree` function and point to the `txt` output folder:

<!-- ```{r eval = FALSE} -->
```{r}
labelfree <- read.labelfree("../../UPS/txt/", reference.experiment = "2500amol", plot = TRUE)
```

This function reads the data, normalises it and calculates ratios to the reference experiment, standard deviations and number of effective observations. We will later use this to build the variance model and likelihood sampling.

### Create the variance model

```{r}
var.model <- variance.model(labelfree)
```

### Sample the likelihood function

```

```

### Analyse the results
